\documentclass{article}
\usepackage[%
    web={usetemplates,pro,usesf},
    aebxmp,eforms,uselayers,
    graphicxsp={showembeds}
]{aeb_pro}
\usepackage[display1]{digicap-pro}
\usepackage{array}

\margins{.25in}{.25in}{24pt}{.25in}                 % left,right,top, bottom
%
% Get the bounding box for 100_0157.eps, trim a little off, and rescale
% to a width of 5in.
%
\setScreensizeFromGraphic[width=5in,trim=0 0 0 108]{./digis/100_0157}

\DeclareDocInfo
{%
    title=Story's Trip to out East,
    author=D. P. Story,
    subject={Digital pics of the trip},
    copyrightStatus=True,
    copyrightNotice={Copyright (C) \the\year, D. P. Story},
    copyrightInfoURL=http://www.acrotex.net
}

\DeclareInitView
{%
    windowoptions={showtitle,fullscreen},
}

\parskip0pt\parindent0pt
\thispagestyle{empty}

\setThumbAppearances[p1]{rgbcolor=red}

\longCapFmt{\bfseries}

\PicsThisDoc
{%
    {p1}{./digis/100_0031}{Gettysburg Battlefield: Seminary Ridge}
        {\footnotesize This shot was taken from seminary
         ridge. You can see the ridge in the distance. I thought of
         the some 60{,}000 casualties that occurred in the fields in
         the foreground.},
    {p2}{./digis/100_0035}{Gettysburg Battlefield: View from Little Round Top}
        {Heavy fighting down below, the Confederates tried on
         several occasions to take this high point.},
    {p3}{./digis/100_0051}{Independence Hall: Desk where G. Washington presided from}
        {This is on our trip through Washington D.C.
         The July day was hot and humid.},
    {p4}{./digis/100_0055}{The Liberty Bell}
        {This is in Philadelphia, the pictures are a
         little out of order.},
    {p5}{./digis/100_0061}{Manhatten in New York City}
        {New York! New York! It's my kind of town,
         Chicago is! Oops, wrong song.},
    {p6}{./digis/100_0075}{New York City: Rockefeller Center}
        {Rockefeller Center, famous place,
         now that I have been there, I've now seen it all!},
    {p7}{./digis/100_0086}{New York City: Ground Zero}
        {\centering September 11, 2001, a day that will
         live in infamy!},
    {p8}{./digis/100_0109}{Statue of Liberty}
        {\footnotesize Give my your tired, your poor,
         your hungry masses yearning to be free\dots},
    {p9}{./digis/100_0141}{Washington D.C.: Jefferson Memorial}
        {\centering The great man himself.},
    {p10}{./digis/100_0142}{Washington D.C.: Jefferson Memorial}
        {\footnotesize\centering A closer look at the great man.},
    {p11}{./digis/100_0157}{Washington D.C.: The Lincoln Memorial}
        {Was there a more nobler man?},
    {p12}{./digis/100_0180}{Washington D.C.: Washington Monument}
        {\centering The first, and some say, the greatest of
         our presidents.},
    {p13}{./digis/100_0224}{Jamestown Colony}
        {On to Jamestown, Virginia, site of the first
         English colony in the new world.},
    {p14}{./digis/100_0207}{Jamestown: Replica of the Discovery}
        {\footnotesize One of three replicas of the ships
         these folks took. This was the final stop on our eastern
         vacation, we enjoyed it and it was educational to
         Alexander.}
}
%
% Use p11 = 100_0157.eps as a background template, but we trim off a little, same as above
% as scale the paperwidth, which is 5in, from the \setScreensizeFromGraphic command.
%
\template[name=p11,width=\paperwidth,transparency={/ca .3},trim=0 0 0 108]{\null}

\begin{document}

\makebox[\linewidth][c]
{\sffamily\bfseries\Large\textcolor{red}{The Story's Trip out East}}

%\useRollovers

% \previewOn

% Order of presentation (the thumbs will be laid out in this order
\presentationOrder{p1,p2,p3,p4,p5,p6,p7,p8,p9,p10,p11,p12,p13,p14}

% default placement for all captions
\dcFirstOpt{vcaption=b,hcaption=c,outerboxsep=0pt}

% for p1, we move the caption to the top
\dcFirstOpt[p1]{vcaption=t,hcaption=c,outerboxsep=0pt}

% Set the display space
\digiDisplaySpace{225pt}{\linewidth}
\vfill
% These are the captions (short form)
\makebox[\linewidth][c]{\insertCaptions}

\vfill
% Insert the thumbs, 2 rows and 7 columns.
\makebox[\linewidth][c]{\insertThumbs{2}{7}}

\end{document}
