\documentclass{article}
\usepackage[usepopup]{ltx4yt}


\hypersetup{pdfpagemode=UseNone,colorlinks,
  pdfencoding=auto,
  pdftitle={The \texorpdfstring{\textsf{ltx4yt} Package\\[3pt]}{ltx4yt Package: }Playing YouTube in a Browser using Forms and JavaScript},
  pdfauthor=D. P. Story,
  pdfsubject={Play YouTube videos in the default browser},
  pdfkeywords={YouTube, AeB}
}
\title{The \texorpdfstring{\textsf{ltx4yt} Package\\[3pt]}{ltx4yt Package: }Playing YouTube videos in a browser using Forms and JavaScript}
\author{D. P. Story}

%\previewOn\pmpvOn

\parindent=0pt\parskip6pt


\begin{popupmenu}{YTMenu}
    \puIdTitle{Select a YouTube Video}{} % A title has no ytId
    \begin{submenu}{title=Music Videos}
        \puIdTitle{Kung-Fu Fighting (Bruce Lee)}{GZ9e3Dy7obA}
        \puIdTitle{Kung-Fu Fighting* (Carl Douglas)}{jhUkGIsKvn0}
        \puIdTitle{Ink Spots - If I didn't care}{rvwfLe6sLis}
        \puIdTitle{Ink Spots* - My Prayer}{h7KJCns5v3g}
    \end{submenu}
    \begin{submenu}{title=Adobe Related Videos}
        \puIdTitle{Open at Adobe}{eNzrn8-JFSE}
        \puIdTitle{Lori's Corner Episode \#1}{5y9-EVmreU4}
        \puIdTitle{Intro to PDF Portfolios}{T9Yzo_hlwP0}
    \end{submenu}
    \begin{submenu}{title=Action Videos}
        \puIdTitle{Rocket Jump}{7XzdZ4KcI8Y}
        \puIdTitle{AimBot}{NYGlWjIKoY4}
        \puIdTitle{Flower Warfare}{031Dshcnso4}
        \puIdTitle{Modern Warfare: Frozen Crossing Pt. 1}{rzQMGMuD1sU}
        \puIdTitle{Modern Warfare: Frozen Crossing Pt. 2}{a08ViuvORRM}
    \end{submenu}
\end{popupmenu}

\begin{popupmenu}{YTSea}
  \puIdTitle{\Esc"Sea Hunt\Esc" US TV series {(1958-61)} lead-in}{Lz0aMoWh8Q4}
  \puIdTitle{Theme Song to Sea Hunt*}{2QxXk6X9GDo}
  \puIdTitle{J\"{u}rgen's favorite song*}{mLDF5MBMWHE}
  \puIdTitle{Learn \cs{LaTeX} in one video}{VhmkLrOjLsw}
\end{popupmenu}


% After defining all menus used with YouTube videos, declare them using \ytUseMenus
\ytUseMenus{YTMenu,YTSea}

\declarePlayList{\playList}{% note: put parentheses within braces
    \ytIdTitle{Kung-Fu Fighting {(Bruce Lee)}}{GZ9e3Dy7obA}
    \ytIdTitle{Kung-Fu Fighting* {(Carl Douglas)}}{jhUkGIsKvn0}
    \ytIdTitle{RAF Sculthorpe {(Watch for my Mom at 6:22!)}}{K7H8QghVs9k}
    \ytIdTitle{Rocket Jump}{7XzdZ4KcI8Y}
    \ytIdTitle{Abdul And Cleopatra* - Jonathan Richman and the Modern Lovers}{mLDF5MBMWHE}
%
    \ytIdTitle{J\"{u}rgen's favorite song*}{mLDF5MBMWHE}
    \ytIdTitle{Learn \cs{LaTeX} in one video}{VhmkLrOjLsw}
    \ytIdTitle{"Sea Hunt" US TV series {(1958-61)} lead-in}{Lz0aMoWh8Q4}
}

\begin{document}

\maketitle

In this second sample file, the combo box and popup menu are
demonstrated. Both of these use JavaScript methods that will
function perfectly on \textsf{Adobe Acrobat}, \textsf{Adobe
Acrobat Reader DC}, and \textsf{PDFX-Change Editor}. None of the fields
work within the native PDF viewer of modern browsers.

\textbf{Demo of combo box of favorites.} By convention of this
package, items with an ``\texttt{*}" in their title is a signal to
the document consumer that that video cannot be
embedded and must be played on the YouTube site with
advertisements and such. \vspace{-\parskip}
\begin{quote}
\ytPlayList{\tops{Kung-Fu Fighting {(Bruce Lee version)}}{GZ9e3Dy7obA}}{\playList}
\ytComboList{YT1}{190bp}{11bp}\olBdry
  \ytComboBtn[\TU{Click to play}]{YT1}{33bp}{11bp}
\end{quote}

\ytPopupBtn{YTMenu}{20bp}{5bp}
\textbf{Demo of a popup menu of favorites.}
On this page, with your mouse cursor, roll over the push button labeled \textcolor{blue}{\textsf{YT Menu}}, and a popup
menu appears. Choose a YouTube video based on title.

\ytPopupBtn[\CA{Sea Hunt}]{YTSea}{20bp}{5bp} Yes, you can have multiple popup menus in the document.

\textbf{Demo of an interactive search}\\[3pt]
\ytInputQuery{1.5in}{11bp}\olBdry
\ytSearch{}{11bp}\olBdry
\ytClearQuery{}{11bp}

\end{document}
