\documentclass{article}
\usepackage[fleqn]{amsmath}
\usepackage[
    web={centertitlepage,designv,forcolorpaper,tight*,latextoc,pro},
    eforms,aebxmp
]{aeb_pro}
\usepackage{eq-save}
\usepackage[ImplMulti]{dljslib}
\usepackage{graphicx,array,fancyvrb}
\usepackage{aeb_mlink}
%\usepackage{myriadpro}
%\usepackage{calibri}
\usepackage[altbullet]{lucidbry}

\def\hardspace{{\fontfamily{cmtt}\selectfont\symbol{32}}}

\usepackage{acroman}
\usepackage[active]{srcltx}

\urlstyle{tt}

\def\STRUT{\rule{0pt}{14pt}}
\useBeginQuizButton[\CA{Begin}]
\useEndQuizButton[\CA{End}]

\makeatletter
\newcount\hesheCnt \hesheCnt=-1
\def\heshe{\@ifstar{\heshei}{\global\advance\hesheCnt1\relax\heshei}}
\def\heshei{\ifodd\hesheCnt she\else he\fi}
\def\HeShe{\@ifstar{\HeShei}{\global\advance\hesheCnt1\relax\HeShei}}
\def\HeShei{\ifodd\hesheCnt She\else He\fi}
\def\hisher{\@ifstar{\hisheri}{\global\advance\hesheCnt1\relax\hisheri}}
\def\hisheri{\ifodd\hesheCnt her\else his\fi}
\def\himher{\@ifstar{\himheri}{\global\advance\hesheCnt1\relax\himheri}}
\def\himheri{\ifodd\hesheCnt her\else him\fi}
\makeatother

\DeclareDocInfo
{
    university={\AcroTeX.Net},
    title={The \textsf{eq-save} Package},
    author={D. P. Story},
    email={dpstory@acrotex.net},
    subject=Documentation for the eq-save package,
    talksite={\url{www.acrotex.net}},
    version={1.2.5, 2019/08/07},
    Keywords={LaTeX, form field, hints, AcroTeX},
    copyrightStatus=True,
    copyrightNotice={Copyright (C) \the\year, D. P. Story},
    copyrightInfoURL={http://www.acrotex.net}
}

\universityLayout{fontsize=Large}
\titleLayout{fontsize=LARGE}
\authorLayout{fontsize=Large}
\tocLayout{fontsize=Large,color=aeb}
\sectionLayout{indent=-62.5pt,fontsize=large,color=aeb}
\subsectionLayout{indent=-31.25pt,color=aeb}
\subsubsectionLayout{indent=0pt,color=aeb}
\subsubDefaultDing{\texorpdfstring{$\bullet$}{\textrm\textbullet}}

\chngDocObjectTo{\newDO}{doc}
\begin{docassembly}
var titleOfManual="The eq-save Package";
var manualfilename="Manual_BG_Print_eq-save.pdf";
var manualtemplate="Manual_BG_Brown.pdf"; // Blue, Green, Brown
var _pathToBlank="C:/Users/Public/Documents/ManualBGs/"+manualtemplate;
var doc;
var buildIt=false;
if ( buildIt ) {
    console.println("Creating new " + manualfilename + " file.");
    doc = \appopenDoc({cPath: _pathToBlank, bHidden: true});
    var _path=this.path;
    var pos=_path.lastIndexOf("/");
    _path=_path.substring(0,pos)+"/"+manualfilename;
    \docSaveAs\newDO ({ cPath: _path });
    doc.closeDoc();
    doc = \appopenDoc({cPath: manualfilename, oDoc:this, bHidden: true});
    f=doc.getField("ManualTitle");
    f.value=titleOfManual;
    doc.flattenPages();
    \docSaveAs\newDO({ cPath: manualfilename });
    doc.closeDoc();
} else {
    console.println("Using the current "+manualfilename+" file.");
}
var _path=this.path;
var pos=_path.lastIndexOf("/");
_path=_path.substring(0,pos)+"/"+manualfilename;
\addWatermarkFromFile({
    bOnTop:false,
    bOnPrint:false,
    cDIPath:_path
});
\executeSave();
\end{docassembly}


\begin{document}

\maketitle

\selectColors{linkColor=black}
\tableofcontents
\selectColors{linkColor=webgreen}


\section{Introduction}

In this documentation, the one reading an \AEB\footnote{{\AcroTeX} eDucation
Bundle} document is referred to as a student, as that is the intended target
audience for education materials developed by the various packages of \AEB.

The \pkg{exerquiz} package defines the \env{oQuestion}, \env{shortquiz}, and
\env{quiz} environments that are used to pose interactive questions to
students. The original concept of \pkg{exerquiz} was as an integral component
in the development of education materials such as digital tutorials or
worksheets. A student may work through such a document, learning concepts and
answering questions to reinforce {\hisher} understanding.

In the past, \app{Adobe Reader} (now \app{Adobe Acrobat Reader})---henceforth
referred to as \app{AR}--- did not save form data; consequently, work done by
the student is lost when the document is closed. In the more recent versions,
beginning perhaps with version~11, \app{AR} can now save form data. The
\pkg{eq-save} package was written at a user's request to save all the quiz
data so that the student does not lose {\hisher} results after saving and
closing the document.

To be clear, when a {\PDF} (by \app{AR}) document is saved, the form data is
also saved: the value of the field and properties of the field, such as
border color, are saved. However, \pkg{exerquiz} keeps running tallies on the
student's progress through the document, these are in the form of JavaScript
variables, arrays and objects; the current values of these are \emph{not
saved} with the document. Therefore, if the student saves the \PDF, it is
necessary to save a minimal amount of information that can later be used to
reconstruct the state of the document at the time student saved and closed the
document. This `state data' is saved to a hidden text field. When the
document is opened again, this hidden field is read, and the state of the
document is minimally restored.

\section{Requirements and options of the package}

The \pkg{eq-save} package, being a support package, requires \pkg{exerquiz},
dated 2017/07/30 or later. Use the package in the usual way,
\begin{Verbatim}[xleftmargin=\amtIndent,commandchars=!()]
\documentclass{article}
\usepackage[!ameta(options)]{exerquiz}
\usepackage[!ameta(options)]{eq-save}
\end{Verbatim}
There are only two options for \pkg{eq-save}, these are \opt{devmode} and
\opt{!devmode}.\marginpar{\small\hfill\mbox{\parbox[t]{\marginparwidth}{\raggedleft
\mbox{Options:\hspace{15pt}} \opt{devmode} \opt{!devmode}}}} As we shall see
below, there is an optional `gatekeeper' command \cs{nameField}. The student
is not allowed to peek at the document until a name is entered (preferably
the student's own name) into the \cs{nameField}. When the \cs{nameField} and
its companion \cs{BeginNoPeeking} are present it is rather inconvenient to
develop the document, create and test quizzes because the author must first
pass the `gatekeeper'. When the \opt{devmode} is in force, entering a name in
\cs{nameField} is no longer required to view the rest of the document. The
other option, \opt{!devmode} is the opposite of \opt{devmode}, that is, when
\cs{nameField} and \cs{BeginNoPeeking} are present in the document, the
student (or author) must enter a name into the name field before viewing the
rest of the document. The \opt{!devmode} option is the default, passing no
option is the same as passing \opt{!devmode}.

\section{Basic commands}

Actually, without any of the supporting commands, yet to be described, the
document may be saved, closed, opened again. The responses to questions
within the \env{oQuestion} and \env{shortquiz} environments are as when they
were saved, the same is true for a full quiz of a \env{quiz} environment. So
what is the need for this document? This package provides \emph{bookkeeping
services}. Before continuing, let's illustrate by example. Answer one of the
\env{shortquiz} questions and answer both questions from the \env{quiz}
environment. Save the document, open and return to the page. When you return
answer (correctly) the other question and/or change the answer for the other
questions.\previewOff
\begin{shortquiz*}[sQz1]
Answer each of these to test your understanding.
\begin{questions}
    \item Select the two mathematicians recognized as the originators of Calculus.\marginpar{\small\raggedleft \emph{Hint:} N\&L}
\begin{manswers}{5}
  \bChoices
    \Ans0 Banach\eAns
    \Ans1 Newton\eAns
    \Ans0 Hilbert\eAns
    \Ans1 Liebniz\eAns
  \eChoices
\end{manswers}
  \item $ 1 + 16 = \RespBoxMath[\rectW{.5in}]{17}{1}{.0001}{[0,1]}\olBdry\relax\CorrAnsButton{17}$
  \item Which of the individuals below is the originator of \TeX?
\begin{answers}{5}
  \bChoices
    \Ans0 Goossens\eAns
    \Ans0 Rahtz\eAns
    \Ans0 Mittelback\eAns
    \Ans0 Lamport\eAns
    \Ans1 Knuth\eAns
  \eChoices
\end{answers}
\end{questions}
\end{shortquiz*}
\noindent
Now complete this quiz consisting of the first two questions above, for simplicity.
\begin{quiz*}{qz1}
Respond to each without error. Passing is 100\%.
\begin{questions}
    \item Select the two mathematicians recognized as the originators of Calculus.
\begin{manswers}{5}
  \bChoices
    \Ans0 Banach\eAns
    \Ans1 Newton\eAns
    \Ans0 Hilbert\eAns
    \Ans1 Liebniz\eAns
  \eChoices
\end{manswers}
  \item $ 1 + 16 = \RespBoxMath[\rectW{.5in}]{17}{1}{.0001}{[0,1]}$
\end{questions}
\end{quiz*}\cgBdry[.5em]\ScoreField\currQuiz\CorrButton\currQuiz\hfill Answers: \AnswerField[\rectW{1in}]\currQuiz\vcgBdry[6pt]
\hfill\ding{172}\enspace\sooField{1in}{11bp}\cgBdry\clearAllField{}{11bp}\vcgBdry[12pt]
The field labeled with `\ding{172}' is one of the new fields, as is the one
to its right. As you work through the above questions, the field keeps track
of your success rate in all quizzes (from the \env{oQuestion},
\env{shortquiz}, and \env{quiz} environments). When you save, close, and open
again, the tally continues where it left off. Ideal for working through a
long document. The field `\textsf{Clear All}' clears all quiz results as well as
the field labeled `\ding{172}', then all is forgotten.

Before continuing on to the discussion of the various commands of this
package, several observations are appropriate.
\begin{itemize}
  \item As soon as you respond to an \emph{immediate-feedback question} (a question
      from either the \env{oQuestion} or \env{shortquiz} environment), the
      total number of questions of this type is known, its 4 for this set of
      questions. In the \textcolor{red}{Quiz}, problem~1 is a multiple
      selection (MS) question with two correct answers; problem~2 has one correct
      answer; problem~3 is multiple choice (MC), only one correct question.
      There is a total of 4 ($\text{two}+\text{one}+\text{one}=4$).
  \item As you answer more immediate-feedback questions, or change your
      answers from a correct ones to an incorrect ones, the tally changes
      appropriately, but always says `out of 4' (in this set of quizzes).
  \item The quiz (as constructed from the \env{quiz} environment) has only
      two questions, but the tally box does not know this until
      `\textsf{Begin}' and `\textsf{End}' are pressed. A quiz consists of
      \emph{delayed-feedback} questions.

  \item Results (for the quiz) are not known until the `\textsf{End}' button
      is pressed, then the tally field `\ding{172}' is updated. You'll note
      that the multiple selection (MS) question only contributes one (1) to
      the `out of' number, that's because MS is scored differently than it is
      for immediate-feedback.

\end{itemize}

\subsection{Bookkeeping commands}\previewOff

The `bookkeeping' commands are create text field to hold ongoing tally data.
\bVerb\takeMeasure{\string\sooField[\ameta{opts}]\darg{\ameta{width}}\darg{\ameta{height}}}%
\setlength\aebscratch{\bxSize}%
\def\1{\makebox[0pt][l]{\hspace{\aebscratch}\enspace\makebox[0pt][l]{\hspace{.5in}\enspace\normalfont(score field)}\sField[\textSize{7}]{.5in}{9bp}}}%
\def\2{\makebox[0pt][l]{\hspace{\aebscratch}\enspace\makebox[0pt][l]{\hspace{.5in}\enspace\normalfont(`out of' field)}\ooField[\textSize{7}]{.5in}{9bp}}}%
\def\3{\makebox[0pt][l]{\hspace{\aebscratch}\enspace\makebox[0pt][l]{\hspace{.5in}\enspace\normalfont(combined score field)}\sooField[\textSize{7}]{.5in}{9bp}}}%
\begin{dCmd}[commandchars=!()]{\bxSize}
!1\sField[!ameta(opts)]{!ameta(width)}{!ameta(height)}
!2\ooField[!ameta(opts)]{!ameta(width)}{!ameta(height)}
!3\sooField[!ameta(opts)]{!ameta(width)}{!ameta(height)}
\end{dCmd}
\eVerb All three field generate a text field with dimensions \ameta{width}
and \ameta{height}, the \meta{opt} allows you to pass \pkg{eforms} field
options to change the appearance of the field. \cs{sField} holds only the number of question answered correctly;
\cs{ooField} holds the `out of' value, the number of questions detected; \cs{sooField} is a combination of
the first two values, typically is displays `3 out of 6'. The `out of' phrase is the expansion of \cs{eqOutOf}, a command
defined and documented in \pkg{exerquiz}. A convenience way of redefining the `out of' phrase is through \cs{declareScorePhrase}:
\bVerb\takeMeasure{\string\declareScorePhrase\darg{\#1+"\string\space\string\eqOutOf\string\space"+\#2}}%
\setlength\aebscratch{\bxSize}%
\def\1{\makebox[0pt][l]{\hspace{\aebscratch}\enspace\normalfont(default definition)}}%
\begin{dCmd}[commandchars=!()]{\bxSize}
\declareScorePhrase{!ameta(JS-str)}
!1\declareScorePhrase{#1+"\space\eqOutOf\space"+#2}
\end{dCmd}
\eVerb The argument \ameta{JS-str} is a JavaScript string. It is phrased using \texttt{\#1} and \texttt{\#2}, which at
compile time, are replaced with JavaScript variables that will hold the score value and the `out of' value.

\newtopic With \pkg{exequiz} you can also assign points for questions in \env{quiz} environments; as a consequence, there is
a similar set of commands to those above.
\bVerb\takeMeasure{\string\psooField[\ameta{opts}]\darg{\ameta{width}}\darg{\ameta{height}}}%
\begin{dCmd}[commandchars=!()]{\bxSize}
\psField[!ameta(opts)]{!ameta(width)}{!ameta(height)}
\pooField[!ameta(opts)]{!ameta(width)}{!ameta(height)}
\psooField[!ameta(opts)]{!ameta(width)}{!ameta(height)}
\end{dCmd}
\eVerb These fields report the point totals. For \env{oQuestion} and \env{shortquiz} environments, each question is only 1 point, but
for \env{quiz} environment you can assign points using the \cs{PTs} command, as illustrated the documentation of \AEB. We do not illustrate
this set of commands in the documentation.

To clear all the fields just described, as well as all fields in the \env{oQuestion}, \env{shortquiz} and
\env{quiz} environment, insert the \cs{clearAllField} into your document.
\bVerb\takeMeasure{\string\clearAllField[\ameta{opts}]\darg{\ameta{width}}\darg{\ameta{height}}}%
\begin{dCmd}[commandchars=!()]{\bxSize}
\clearAllField[!ameta(opts)]{!ameta(width)}{!ameta(height)}
\end{dCmd}
\eVerb The interpretation of the parameters are as above.


\subsection{Gatekeeper commands}

The application that inspired this package was the Professor of the course did not want the student to look at the quizzes
until {\heshe} entered {\hisher*} name. As a result, should you want this sort of `security', include the \cs{nameField}
and \cs{BeginNoPeeking} commands. The latter should begin on the first page you don't want your students to look upon until
they enter their names.
\bVerb\takeMeasure{\string\flJSStr[noquotes,noparens]\darg{\string\EnterNameFirstMsg}\darg{\ameta{msg}}}%
\begin{dCmd}[commandchars=!()]{\bxSize}
\nameField[!ameta(opts)]{!ameta(name)}{!ameta(width)}{!ameta(height)}
\BeginNoPeeking
!STRUT\flJSStr[noquotes,noparens]{\EnterNameFirstMsg}{!ameta(msg)}
\end{dCmd}
\eVerb The \meta{name} field allows you to enter a personalized field name,
such as `\texttt{IhrName}', or something. The other parameters are the same
as above and are described briefly in the description of \cs{sField}.

When the student enters {\hisher} name, the document is cleared: all fields
that support questions from the \env{oQuestion}, \env{shortquiz}, and
\env{quiz} environments; all fields whose commands begin with `s', `oo',
`soo', `ps', `poo', and `psoo' fields, as described above. This is a weak
security measure to make it more difficult for a student to just take the
worksheet of an `A' student and simply remove the name and enter {\hisher}
own name. Of course, unless students supervised in a lab, these measures are
only inconveniences.

There are two JavaScript strings that can be rephrased or localized. The default
declarations are,
\begin{Verbatim}[xleftmargin=\amtIndent,commandchars=!()]
\flJSStr[noquotes,noparens]{\EnterNameFirstMsg}
!qquad{You must enter your name first!}
!STRUT\dlJSStr{\eqerrUnfinishQuizAtSave}{One of your quizzes
!qquad(is not finished, you will lose those responses.)}

\end{Verbatim}

\section{Demonstration files}

There are two sample files, \texttt{eqsave-name.tex} and
\texttt{eqsave-noname.tex}, found in the \texttt{examples} folder. The first
has uses the gatekeeper commands (these are \cs{sField} and \cs{BeginNoPeeking}), while the
second one does not; otherwise, the files are the same.

\section{My retirement}

Now, I simply must get back to it. \dps

\end{document}
