\documentclass{article}
% aeb_pro  not required for pdflatex, lualatex, or xelatex
% If you don't have acrobat, no harm is done. For the
% dvips -> distiller workflow, aeb_pro is required.
\usepackage[web={extended,forcolorpaper},eforms,useacrobat]{aeb_pro} %,forcolorpaper
% for non-pdfmark workflow, the alternative is to use
% the following two packages instead.
%\usepackage[extended]{web}
%\usepackage{eforms}
\usepackage[%
  !nonrandomized,
  showletters,
  !showanswerkey,
  savedata,
  lang=custom,
]{dps}

%\usepackage{graphicx}

\ifeqforpaper\setlength{\oddsidemargin}{-.5in}\fi


%\previewOn \pmpvOn
%\useRandomSeed{number}
\inputRandomSeed
%\useLastSeed

\margins{.5in}{.5in}{.5in}{.5in} % left,right,top, bottom
\screensize{11in}{8.5in} % height, width

\DeclareDocInfo
{
    title=Stat Matching Game,
    author=D. P. Story,
    university=NORTHWEST FLORIDA STATE COLLEGE\\Department of Mathematics,
    email=storyd@nwfsc.edu,
    subject=First extra credit assignment,
    keywords={statistics, matching, game},
    talksite=http://www.acrotex.net,
    copyrightyears=2006-\the\year,
}
\talkdateLabel{Version}
\version{1.0}\nocopyright

\everyTextField{\textFont{TiRo}}

% Try to prevent the student from saving the game (for some other student)
% we clear the game board if either student closes or save the document.
\clearOnCloseOrSave

\optionalPageMatter
{%
    \par\minimumskip\vspace{\stretch{1}}
    \begin{center}
    \fcolorbox{blue}{white}{%
    \begin{minipage}{.75\linewidth}\parskip3pt
    \textbf{\textcolor{red}{Instructions: }}
    On the next page of this document is a little matching game covering
    some of the statistical concepts discussed in class.
    \begin{itemize}
        \item When you turn to the next page, type in your name in the name field
        provided near the top of the page.
        \item Follow the instructions on that page on how to answer the questions.
        \item After you have correctly answered the last question correctly, a message
        appears at the bottom of the page with an evaluation of your effort.
        \item Print the completed page and turn it in to me at the next class meeting
        for (extra) credit.
    \end{itemize}
    \textbf{\textcolor{red}{Warning:}} The puzzle board is cleared if this document
    is closed or saved. Complete the puzzle in one sitting, then print the results.
    \end{minipage}}
    \end{center}
}

\rheader{}

\parindent0pt
\parskip6pt

\DeclarePuzzle
{%
    {R}{R}
    {o}{o}
    {n}{n}
    {a}{a}
    {l}{l}
    {d}{d}
    {}{space}
    {F}{F}
    {i}{i}
    {s}{s}
    {h}{h}
    {e}{e}
    {r}{r}
}


%\writeComposingEnv

\begin{Composing}

\begin{cQ}{R}
The two branches of statistics
are descriptive and \underbar{\hspace{.5in}}.
\end{cQ}
\begin{cA}[r]{R}
inferential
\end{cA}

\begin{cQ}{o}
\underbar{\hspace*{.5in}} is the
science of collecting, organizing, analyzing and interpreting data
in order to make decisions.
\end{cQ}
\begin{cA}{o}
statistics
\end{cA}

\begin{cQ}{n}
A frequency distribution is an example of
\underbar{\hspace*{.5in}}
\end{cQ}
\begin{cA}{n}
data reduction
\end{cA}

\begin{cQ}{a}
Find the median of the following
data:\par
\begin{tabular}{r|ll}
2&2334&\kern6pt Key $2\,|\,4=24$\\
2&57888\\
3&344\\
3&55666\\
4&0023\\
4&566
\end{tabular}
\end{cQ}
\begin{cA}{a}
$34.5$
\end{cA}

\begin{cQ}{l}
Given that $n=5$,
$\sum x = 26$ $\sum x^2 = 154$, compute $\bar x$ and $s$.
\end{cQ}
\begin{cA}{l}
$5.2$ and $2.17$
\end{cA}
\begin{cQ}{d}
A \underbar{\hspace{.5in}} is a sample
in which every possible sample of the same size has the same chance
of being selected.
\end{cQ}
\begin{cA}{d}
simple random sample
\end{cA}

\begin{cQ}{F}
The number \underbar{\hspace{.5in}} divides a data set in such a way that
$75\%$ of the data is less than it and $25\%$ of the data is greater
than it.
\end{cQ}
\begin{cA}[f]{F}
$Q_3$
\end{cA}

\begin{cQ}{i}
\underbar{\hspace{.5in}} is the measure of central tendency
that is sensitive to outliers in the data set.
\end{cQ}
\begin{cA}{i}
sample mean
\end{cA}

\begin{cQ}{s}
$\mu$ refers to the \underbar{\hspace{.5in}}
\end{cQ}
\begin{cA}{s}
population mean
\end{cA}
\begin{cQ}{h}
In a data set with sample
mean of $4.5$ and sample standard deviation of $1.5$, the $z$-score
of $x = 4$ is $ z = \underbar{\hspace{.5in}}$.
\end{cQ}
\begin{cA}{h}
$-0.33$
\end{cA}

\begin{cQ}{e}
If a $z$-score of a data
entry is negative, then that data entry is
\underbar{\hspace{.5in}} than mean.
\end{cQ}
\begin{cA}{e}
less
\end{cA}

\begin{cQ}{r}
The mean value of land and building
per acre from a sample of farms is $\$1200$ with a standard
deviation of $\$350$. Assuming the distribution of the data set is
bell shaped, approximately what percentage of the sample of farmers
had value of land and building (per acre) between $\$1200$ and
$\$1550$?
\end{cQ}
\begin{cA}{r}
$34$
\end{cA}

%-------------------

\begin{cA}[b]{fake1}
$5.2$ and $1.94$
\end{cA}

\begin{cA}[c]{fake2}
sample
\end{cA}

\begin{cA}[d]{fake3}
$0.33$
\end{cA}

\begin{cA}[g]{fake4}
greater
\end{cA}

\begin{cA}[j]{fake5}
median
\end{cA}

\begin{cA}[k]{fake6}
mode
\end{cA}

\begin{cA}[m]{fake7}
$Q_1$
\end{cA}

\begin{cA}[p]{fake8}
variance
\end{cA}

\begin{cA}[t]{fake9}
$35$
\end{cA}

\end{Composing}

\begin{document}

%\maketitle


\def\answidth{1.7in}
\def\queswidth{2in}

\ifeqforpaper
\vspace*{-4\baselineskip}\fi

{\bfseries\noindent
\makebox[\textwidth]{\rlap{STA 2023}\hfill\textcolor{blue}{\webtitle}\hfill\llap{Statistics}}
\makebox[\textwidth]{\rlap{\webauthor}\hfill\textcolor{blue}{Descriptive Statistics}\hfill\llap{Fall 2006}}}

\underbar{\textbf{Name:} \textField[\BC{}]{dpsSignInName}{2in}{11bp}}

\textcolor{red}{\textbf{Instructions:}} Select a question from the
left panel by clicking its checkbox. Find the answer listed in
either the right panel.  No guessing! A maximum of $\dsthreshold$
tries on any problem before you get $\dspenaltypoints$ penalty
points!  Passing is to complete the puzzle with only $\dspassing$
incorrect answers.

\fbox{\begin{minipage}{\linewidth-2\fboxsep-2\fboxrule}
Who is considered the founder of modern statistics? The answer is
hidden in the puzzle below.\par\smallskip
\begin{center}
\insertPuzzle{13}
\end{center}
\kern3pt
\end{minipage}}%

\fbox{\begin{minipage}[t][5.25in+3\baselineskip][t]{\linewidth-\answidth-2\fboxsep-2\fboxrule}\raggedright
\makebox[\linewidth]{\centering\textbf{Questions}}
\begin{enumerate} 
\displayRandomizedQuestions
\end{enumerate}
\end{minipage}}%
%
\fbox{\begin{minipage}[t][5.25in+3\baselineskip][t]{\answidth-2\fboxsep-2\fboxrule}\raggedright
\makebox[\linewidth]{\textbf{Answers}}
\begin{itemize}\itemsep0pt
\displayRandomizedAnswers
\end{itemize}
\par\smallskip
\end{minipage}}%

\ifeqforpaper\else
\textbf{\textcolor{red}{Important:}} Don't forget to print the puzzle page and to hand it in to me.

Print this page: \printDPS{}{11bp}\cgBdry[1ex]
Try again: \resetDPS{}{11bp}
\fi


\end{document}
