\documentclass{article}
\usepackage{amstext}
\usepackage{web}
\usepackage[usesumrytbls]{exerquiz}
\usepackage[usebatch]{thorshammer}

\DeclareQuiz{q1}

\setInitMag{fitwidth}
\hypersetup{pdfpagemode=UseNone} % don't need to see bookmarks
\hypersetup{pdfpagelayout=OneColumn}
\reversemarginpar

\showCreditMarkup

%\previewOn\pmpvOn

\useBeginQuizButton[\CA{Begin}]
\useEndQuizButton[\CA{End}]

\PTsHook{($\eqPTs^{\text{pts}}$)}
\useMCCircles

% Neither of the two CFG files here uses the second star option, see theexcfg2-star.tex
% Adjust \instrPath \classPath in CFG file as needed
% Two methods illustrated here
%\InputFormattedClass{thorsclass2}

\newcommand\ParseClassLine[4]{\classMember{#1}{#2}{#4}}
\InputFormattedClass[\ParseClassLine]{thorsclass3}

% \autoCopyOff

%\distrToStudentsOff

\begin{makeClassFiles}
\sadQuizzes
\end{makeClassFiles}

\begin{document}


\thQuizHeader

\noindent\textbf{Instructions:}
\begin{itemize}
\item (For the student) Press `\textsf{Start}' to begin the
    quiz, after you've completed the quiz, press
    `\textsf{End}'. \emph{Save the document before closing
    it}.
\item (For the instructor) Open the document the student has
    saved, the `\textsf{Mark It}' and `\textsf{Freeze Quiz}'
    are visible. Press the `\textsf{Mark It}' button and the
    quiz will be marked. For the extended response questions,
    enter the points assigned in the box in the left margin.
    At your option, reset the quiz or save the quiz with the
    markup.
\end{itemize}

\begin{quiz*}{\currQuiz}
Solve each of these problems, passing is 100\%.
\begin{questions}
  \item\PTs{3} Which of these are true ?
\begin{answers}{4}
\Ans1 True & \Ans0 False
\end{answers}

  \item \PTs{4} Select which of the following is true.
\begin{answers}{4}
\Ans1 True & \Ans0 False & \Ans0 Maybe & \Ans0 Sometimes
\end{answers}

  \item\PTs{2} $9+8=\RespBoxMath{17}{1}{.0001}{[0,1]}$

\essayQ{5} % num points assigned
\item\PTs{5} Write a short history of Acro\negthinspace\TeX.\par
\RespBoxEssay{\linewidth}{1in}

\item\PTs{3} Which of the following are numbers?
\begin{manswers}{6}
\bChoices
  \Ans[-1]{0}d\eAns
  \Ans[1]{1}17\eAns
  \Ans[-1]{0}p\eAns
  \Ans[1]{1}88\eAns
  \Ans[-1]{0}s\eAns
  \Ans[1]{1}105\eAns
\eChoices
\end{manswers}

\multipartquestion

    \item\PTs{20} Answer each of the following multiple selection problems. Each correct answer
    is worth $3$ points, and each incorrect answer is worth $-2$ points.
    \begin{questions}

\rowsep{3pt}

        \item\PTs{9} Select which people who served as a President
                     of the United States. (Select all correct choices.)

        \begin{manswers}*{2}%
            \bChoices
                \Ans[-2]{0} Henry Clay\eAns
                \Ans[-2]{0} Ben Franklin\eAns
                \Ans[3]{1}\label{aj} Andrew Jackson\eAns
                \Ans[3]{1}\label{rr} Ronald Reagan\eAns
                \Ans[-2]{0} George Meade\eAns
                \Ans[3]{1}\label{gc} Grover Cleveland\eAns
                \Ans[-2]{0} John Jay\eAns
                \Ans[-2]{0} Paul Revere\eAns
            \eChoices
        \end{manswers}

\rowsep{3pt}

        \item\PTs{9} Select which people who served as a Chancellor of the
            German Republic. (Select all correct choices.)
        \begin{manswers}*{2}%
            \bChoices[2]
                \Ans[-2]{0} Gustav Heinemann\eAns
                \Ans[-2]{0} Theodor Heu{\ss}\eAns
                \Ans[3]{1} Konrad Adenauer\eAns
                \Ans[-2]{0} Richard von Weizs\"{a}cker\eAns
                \Ans[3]{1} Willy Brandt\eAns
                \Ans[-2]{0} Heinrich L\"{u}bke\eAns
                \Ans[-2]{0} Roman Herzog\eAns
                \Ans[3]{1} Ludwig Erhard\eAns
            \eChoices
        \end{manswers}

\rowsep{3pt}

      \item\PTs{2} If you select all choices in part~(a), you will
          receive -1 points as a penalty for bad guessing. \textbf{Question:}
          Determine the \emph{number of correct choices} in part~(a)?
          \begin{answers}{4}
          \bChoices
            \Ans0 1\eAns
            \Ans0 2\eAns
            \Ans1 3\eAns
            \Ans0 4\eAns
            \Ans0 5\eAns
            \Ans0 6\eAns
            \Ans0 7\eAns
            \Ans0 8\eAns
          \eChoices
          \end{answers}
    \end{questions}

%\essayQ{3} % num points assigned
%\item\PTs{3} Comment on the experience of taking a quiz the `Thorsten way.'.\par
%\RespBoxEssay{\linewidth}{1in}

\end{questions}
\writeProListAux
\end{quiz*}\quad\thQuizTrailer
\end{document} 